Model Walkthru for Peloquin & Frank (2016)

### 2017-10-22 paper01_peloquin_frank2016/model_walkthru/paper01_peloquin_frank2016.rmd
fix a few things start playing around

costs <- c(none=0, some=0, all=0)
priors <- rnorm(nrow(semantics_matrix), mean=.5, sd=.1)
alpha <- 1

@@

# need to make sure length matches nrow 
priors <- rnorm(nrow(input_matrix), mean=.5, sd=.1)

@@

>>>>

# dnorm(), qnorm(), pnorm() 
# hist(rnorm(1000, mean=100, sd=1))

# priors <- normVec(rnorm(nrow(semantics_matrix), mean=.5, sd=.1))
costs <- c(none=0, some=0, all=0)
priors <- rep(.2, 5)
alpha <- 1

@@

# need to make sure length matches nrow 
# priors <- rnorm(nrow(input_matrix), mean=.5, sd=.1) 
priors <- rep(.2, nrow(input_matrix))

@@

```{r}
### THIS CHUNK IS JUST A SANDBOXXXE -----

# carve out a subset
NSA <- pf_data %>% 
  filter(dataset=="pf5") %>%
  filter(scale=="some_all") %>% 
  select(-exp, -scale, -dataset) %>% 
  select(stars, words, study1, study2, speaker.p) %>% 
  arrange(stars, words)

# this is the semantic representation (prob dist) of each scalar item 
NSA_matrix <- NSA %>% 
  # study1 or study2 or speaker.p -- still not sure which col! 
  select(stars, words, value=study1) %>% 
  tidyr::spread(words, value) %>% 
  set_rownames(.$stars) %>%  # `stars` now encoded as rownames
  select(none, some, little, most, all) %>% 
  as.matrix()

# need to make sure length matches ncol
costs <- setNames(rep(0, ncol(NSA_matrix)), nm=colnames(NSA_matrix))

# need to make sure length matches nrow 
priors <- normVec(rep(1, nrow(NSA_matrix)))

# parameter that fixes "how much the cost matters" 
alpha <- 1

# run an iteration
NSA_pragmatics <- fullRecursion(NSA_matrix, costs, priors, alpha)

# visualize result
make_rsa_plot(NSA_matrix, NSA_pragmatics)
```

### 3.4 Steps for doing one full iteration
